The Calibration Reference Data System

### 2016-03-16 docs/paper/response.txt

As far as the implications regarding databases go, we have not expanded on that.
This is mainly because some issues are arguably self evident (distributing
software that requires databases certainly does impose a significantly larger 
burden on those installing and maintaining such a system; we doubt that is 
controversial).

We also think it is nearly self evident that SQL does not always represent 
rules in a clear or easy to understand way (and many astronomers, the ones 
that ultimately must provide those rules, are not experts in SQL, particularly
complex SQL). We aren't saying it is impossible to use only SQL, just not 
ideal. Indeed, Gemini's experience found it to be too constricting (as we did).
Chandra doesn't use it at all, and it appears Spitzer's needs are not as complex.
This is probably aided by the fact that they generally process the data in 
large runs, i.e,. their updates are relatively infrequent as we understand 
it.  Besides, they sometimes have special processing after the query (e.g., 
interpolation between two reference files), so it isn't a pure database
solution either. Accomodating new needs requires new software changes.
To be fair, so does ours if a new kind of rule is required, but that
is much less likely, and much more likely to be in adding a new module
rather than changing existing code.

It really isn't our intent to argue that databases are not appropriate; rather 
for the features we sought, that they did not appear to be the simplest
solution. In things like this, proving it beyond any question is not
something that projects have the resources to do. Indeed, practically 
speaking, there never is proof, only indications by the absense of
solutions using them. The only proof possible is proving that they
are suitable by implementing a system that has the features we sought
using a database. Doing that really is for someone else to do. We can 
only note that we haven't found one in existance yet.

As to the focus on STScI needs. We don't agree that only one page
is devoted to generic needs. We would argue that the great majority
of the discussion is directed to generic capabilities, particularly
with regard to the bestref core functionality, with occasional
references to how they relate to JWST or HST. Yes, the examples are for
STScI systems, but it would be odd for us to use examples for other
observatories for which we are not qualified to provide. We don't 
believe that these examples in any way limit the generic aspects of
the system.
